Model LF

### 2022-10-31 Estimation.Rmd
Commit

>>>>

### Prod 33

```{r}
reg_prod_start=dynlm(TSDELTALOG(prodk_ds) ~ 1 + L(TSDELTALOG(prodk_ds),1:4) +  L(TSDELTALOG(yk_ds),0:4) +  L(TSDELTALOG(rw_ds),0:4)  + L(log(prodk_ds),1) + L(log(yk_ds),1) + L(log(rw_ds),1))

 prod_vars_1 <- str_c("L(TSDELTALOG(prodk_ds), 1:4)", c(3:4))
 yk_ds_vars_1 <- str_c("L(TSDELTALOG(yk_ds), 0:4)", c(1:4))
  rw_ds_vars_1 <- str_c("L(TSDELTALOG(rw_ds), 0:4)", c(1:3))

vars_out_1 <- c( prod_vars_1,ur_ds_vars_1, rw_ds_vars_1 )
vars_out_1

```{r}
reg_prod=dynlm(TSDELTALOG(prodk_ds) ~ 0 + L(TSDELTALOG(prodk_ds),1:2) +  L(TSDELTALOG(yk_ds),0) +  L(TSDELTALOG(rw_ds),c(0,4))  + L(log(prodk_ds),1) + L(log(yk_ds),1) + L(log(rw_ds),1))

### Prod 4

**Growth rates**

```{r}
g_yk_ds= TSDELTALOG(yk_ds)
g_prod_ds= TSDELTALOG(prodk_ds)

test_reg= dynlm(g_prod_ds ~ 1 + g_yk_ds + L(g_yk_ds,1) + L(g_prod_ds,1))
summary(test_reg)

n= (0.85800824 + -0.26114940)/(1-0.28614226)
```
